---
title: "Project_V1"
format: 
  html: 
    embed-resources: true
    code-fold: true
    df_print: paged
editor: visual
---

```{r}
#| message: false
#| warning: false
suppressPackageStartupMessages(library(readxl))
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(plotly))
suppressPackageStartupMessages(library(fmsb))

data = read_excel("Project_1_Data.xlsx", sheet = "pooled123")

filteredData = select(data, Date, PID, BSSQ_1:BSSQ_16, ASSQ_1:ASSQ_16, age, VRexperience, ssq_full, gender, sm)
#we only want to look at those that did not undergo social modelling conditions
filteredData = subset(filteredData, sm == "NO_SM")

#calculating differences between baseline and active SSQ for each symptom
filteredData = mutate(filteredData, d_discomfort = ASSQ_1 - BSSQ_1)
filteredData = mutate(filteredData, d_fatigue = ASSQ_2 - BSSQ_2)
filteredData = mutate(filteredData, d_headache = ASSQ_3 - BSSQ_3)
filteredData = mutate(filteredData, d_eyestrain = ASSQ_4 - BSSQ_4)
filteredData = mutate(filteredData, d_difficulty_focusing = ASSQ_5 - BSSQ_5)
filteredData = mutate(filteredData, d_salivation = ASSQ_6 - BSSQ_6)
filteredData = mutate(filteredData, d_sweating = ASSQ_7 - BSSQ_7)
filteredData = mutate(filteredData, d_nausea = ASSQ_8 - BSSQ_8)
filteredData = mutate(filteredData, d_difficulty_concentrating = ASSQ_9 - BSSQ_9)
filteredData = mutate(filteredData, d_fullness_of_head = ASSQ_10 - BSSQ_10)
filteredData = mutate(filteredData, d_blurred_vision = ASSQ_11 - BSSQ_11)
filteredData = mutate(filteredData, d_dizziness_o = ASSQ_12 - BSSQ_12)
filteredData = mutate(filteredData, d_dizziness_c = ASSQ_13 - BSSQ_13)
filteredData = mutate(filteredData, d_vertigo = ASSQ_14 - BSSQ_14)
filteredData = mutate(filteredData, d_stomach_awareness = ASSQ_15 - BSSQ_15)
filteredData = mutate(filteredData, d_burping = ASSQ_16 - BSSQ_16)


#reclasss VR experience as factor (was chr)
filteredData$VRexperience = as.factor(filteredData$VRexperience)

#we want to filter this data even further and split it into age groups
#once in age groups, calculate the mean change for each of the age groups for each symptom
filteredData = mutate(filteredData, age_group = case_when(
  age >= 16 & age <= 21 ~ "16 to 21",
  age >= 22 & age <= 29 ~ "22 to 29",
  age >= 30 & age <= 37 ~ "30 to 37",
  age >= 38 & age <= 45 ~ "38 to 45",
  age > 45 ~ "above 45"
))

#convert the age groups into factors
filteredData$age_group = as.factor(filteredData$age_group)

#renaming columns to be more informative
names(filteredData)[names(filteredData) == 'BSSQ_1'] <- 'BSSQ_discomfort'
names(filteredData)[names(filteredData) == 'BSSQ_2'] <- 'BSSQ_fatigue'
names(filteredData)[names(filteredData) == 'BSSQ_3'] <- 'BSSQ_headache'
names(filteredData)[names(filteredData) == 'BSSQ_4'] <- 'BSSQ_eyestrain'
names(filteredData)[names(filteredData) == 'BSSQ_5'] <- 'BSSQ_difficulty_focusing'
names(filteredData)[names(filteredData) == 'BSSQ_6'] <- 'BSSQ_salivation'
names(filteredData)[names(filteredData) == 'BSSQ_7'] <- 'BSSQ_sweating'
names(filteredData)[names(filteredData) == 'BSSQ_8'] <- 'BSSQ_nausea'
names(filteredData)[names(filteredData) == 'BSSQ_9'] <- 'BSSQ_difficulty_concentrating'
names(filteredData)[names(filteredData) == 'BSSQ_10'] <- 'BSSQ_fullness_of_head'
names(filteredData)[names(filteredData) == 'BSSQ_11'] <- 'BSSQ_blurred_vision'
names(filteredData)[names(filteredData) == 'BSSQ_12'] <- 'BSSQ_dizziness_o'
names(filteredData)[names(filteredData) == 'BSSQ_13'] <- 'BSSQ_dizziness_c'
names(filteredData)[names(filteredData) == 'BSSQ_14'] <- 'BSSQ_vertigo'
names(filteredData)[names(filteredData) == 'BSSQ_15'] <- 'BSSQ_stomach_awareness'
names(filteredData)[names(filteredData) == 'BSSQ_16'] <- 'BSSQ_burping'





names(filteredData)[names(filteredData) == 'ASSQ_1'] <- 'ASSQ_discomfort'
names(filteredData)[names(filteredData) == 'ASSQ_2'] <- 'ASSQ_fatigue'
names(filteredData)[names(filteredData) == 'ASSQ_3'] <- 'ASSQ_headache'
names(filteredData)[names(filteredData) == 'ASSQ_4'] <- 'ASSQ_eyestrain'
names(filteredData)[names(filteredData) == 'ASSQ_5'] <- 'ASSQ_difficulty_focusing'
names(filteredData)[names(filteredData) == 'ASSQ_6'] <- 'ASSQ_salivation'
names(filteredData)[names(filteredData) == 'ASSQ_7'] <- 'ASSQ_sweating'
names(filteredData)[names(filteredData) == 'ASSQ_8'] <- 'ASSQ_nausea'
names(filteredData)[names(filteredData) == 'ASSQ_9'] <- 'ASSQ_difficulty_concentrating'
names(filteredData)[names(filteredData) == 'ASSQ_10'] <- 'ASSQ_fullness_of_head'
names(filteredData)[names(filteredData) == 'ASSQ_11'] <- 'ASSQ_blurred_vision'
names(filteredData)[names(filteredData) == 'ASSQ_12'] <- 'ASSQ_dizziness_o'
names(filteredData)[names(filteredData) == 'ASSQ_13'] <- 'ASSQ_dizziness_c'
names(filteredData)[names(filteredData) == 'ASSQ_14'] <- 'ASSQ_vertigo'
names(filteredData)[names(filteredData) == 'ASSQ_15'] <- 'ASSQ_stomach_awareness'
names(filteredData)[names(filteredData) == 'ASSQ_16'] <- 'ASSQ_burping'


#isolating the data dictionary
data_dict = read_excel("Project_1_Data.xlsx", sheet = "data_dictionary")

#filter into groups with experience or not
withVRexperience = filter(filteredData, VRexperience == 'Yes')
noVRexperience = filter(filteredData, VRexperience == 'No')

#taking averages for with/without experience
yes_avg_d_discomfort = mean(withVRexperience$d_discomfort)
yes_avg_d_fatigue = mean(withVRexperience$d_fatigue)
yes_avg_d_headache = mean(withVRexperience$d_headache)
yes_avg_d_eyestrain = mean(withVRexperience$d_eyestrain)
yes_avg_d_difficulty_focusing = mean(withVRexperience$d_difficulty_focusing)
yes_avg_d_salivation = mean(withVRexperience$d_salivation)
yes_avg_d_sweating = mean(withVRexperience$d_sweating)
yes_avg_d_nausea = mean(withVRexperience$d_nausea)
yes_avg_d_difficulty_concentrating = mean(withVRexperience$d_difficulty_concentrating)
yes_avg_d_fullness = mean(withVRexperience$d_fullness_of_head)
yes_avg_d_vision = mean(withVRexperience$d_blurred_vision)
yes_avg_d_dizziness_o = mean(withVRexperience$d_dizziness_o)
yes_avg_d_dizziness_c = mean(withVRexperience$d_dizziness_c)
yes_avg_d_vertigo = mean(withVRexperience$d_vertigo)
yes_avg_d_stomach = mean(withVRexperience$d_stomach_awareness)
yes_avg_d_burping = mean(withVRexperience$d_burping)


no_avg_d_discomfort = mean(noVRexperience$d_discomfort)
no_avg_d_fatigue = mean(noVRexperience$d_fatigue)
no_avg_d_headache = mean(noVRexperience$d_headache)
no_avg_d_eyestrain = mean(noVRexperience$d_eyestrain)
no_avg_d_difficulty_focusing = mean(noVRexperience$d_difficulty_focusing)
no_avg_d_salivation = mean(noVRexperience$d_salivation)
no_avg_d_sweating = mean(noVRexperience$d_sweating)
no_avg_d_nausea = mean(noVRexperience$d_nausea)
no_avg_d_difficulty_concentrating = mean(noVRexperience$d_difficulty_concentrating)
no_avg_d_fullness = mean(noVRexperience$d_fullness_of_head)
no_avg_d_vision = mean(noVRexperience$d_blurred_vision)
no_avg_d_dizziness_o = mean(noVRexperience$d_dizziness_o)
no_avg_d_dizziness_c = mean(noVRexperience$d_dizziness_c)
no_avg_d_vertigo = mean(noVRexperience$d_vertigo)
no_avg_d_stomach = mean(noVRexperience$d_stomach_awareness)
no_avg_d_burping = mean(noVRexperience$d_burping)


#taking averages for different age groups
grp1 = filter(filteredData, age_group == '16 to 21')
grp2 = filter(filteredData, age_group == '22 to 29')
grp3 = filter(filteredData, age_group == '30 to 37')
grp4 = filter(filteredData, age_group == '38 to 45')
grp5 = filter(filteredData, age_group == 'above 45')

mean_sqq_ages = c(mean(grp1$ssq_full),
                  mean(grp2$ssq_full),
                  mean(grp3$ssq_full),
                  mean(grp4$ssq_full),
                  mean(grp5$ssq_full)
                  )

data_by_age_group = data.frame(
  age_group = c("16 to 21", '22 to 29','30 to 37','38 to 45','Above 45'),
  mean_ssq = mean_sqq_ages
  
)

filteredData = mutate(filteredData, "generation" = case_when(year(Date) - age >= 2010 ~ "a", year(Date) - age >= 1997 ~ "Z", year(Date) - age >= 1981 ~ "Y", year(Date) - age >= 1965 ~ "X", TRUE ~ "Old"))

```

## Summary of Findings

(executive summary goes here)

## Initial Data Analysis (IDA)

**Source**

Our data was sourced from Cosette Saunder's paper "[Socially Acquired Nocebo Effects Generalize but Are Not Attenuated by Choice](https://drive.google.com/file/d/1stc1Yj0-3ZDLqM31Mf-WKOIVdQYb4TkP/view)".

**Structure**

We specifically looked at participants that did not undego any social modelling; 69 participants, each with 51 variables recorded. Our project focused the following variables:

-   Baseline SSQ (`BSSQ`), Active SSQ (`ASSQ`), and `SSQ_Full`of 16 symptoms (*quantitative, discrete)*: self-reported symptom severity before and after undergoing VR respectively, on a scale of 1 to 10.

-   Participants' `VRexperience` (*qualitative, nominal)*; sorted by experience to see how symptoms differed.

-   `age` of participants (quantitative*, discrete)*; they were then sorted into `age groups`.

-   The change ($\Delta$) between `BSSQ` and `ASSQ` was calculated for each participant for each symptom, and we took the average $\Delta$ for each symptom for each group (`VRexperience` and `age_group`) (*quantitative, discrete).*

::: panel-tabset
## Age Groups

```{r}
#| label: Age groups pie chart
data_age_groups = select(filteredData, age_group)
groups_counted = data_age_groups %>% count(age_group)

age_pie = plot_ly(groups_counted, labels = ~age_group, values = ~n,
                 type = 'pie', direction = 'clockwise', sort = FALSE, rotation = 30)
age_pie <- age_pie %>% layout(title = 'Distribution of ages',
                            showlegend = TRUE)
age_pie
```

## VR Experience

```{r}
#| label: VR experience pie chart

data_experience = select(filteredData, VRexperience)
exp_counted = data_experience %>% count(VRexperience)

vr_pie = plot_ly(exp_counted, labels = ~VRexperience, values = ~n,
                 type = 'pie')
vr_pie <- vr_pie %>% layout(title = 'Distribution of VR experience',
                            showlegend = TRUE)

vr_pie
```
:::

**Limitations**

-   *Self-reporting bias* for both `BSSQ` and `ASSQ` which makes the values prone to being over or underestimates by each participant.

-   `VRexperience` is a binary qualitative classification, it is not descriptive of the nature, amount or frequency, and that those with more than 10 VR experiences were excluded.

# [Research Question]{.underline}

## **What is the effect of past VR experience on the symptoms experienced by people?**

```{r}
#| label: Boxplot of full_ssq vs experience
#| message: false
#| warning: false

plt = ggplot(filteredData, aes(x = VRexperience, y = ssq_full, fill = VRexperience)) +
  geom_boxplot() +
  theme_minimal() +
  labs(x = "VR Experience", y = "Full SSQ")
ggplotly(plt)
```

Those with and without VR experience reported varied severity of symptoms. Interestingly, the VR experienced group saw a greater median `ssq_full`, at 7.0 compared to -0.5 for those without experience, indicating those with experience reported more severe symptoms afterwards. VR experienced participants also showed a greater IQR than those without, at 16.25 and 8.5 respectively, pointing to experienced users reporting less consistent symptom severity.

```{r}
#| label: Experience and symptoms spider chart
#| message: false
#| warning: false
library(plotly)

yes_means = c(yes_avg_d_discomfort,
              yes_avg_d_fatigue,
              yes_avg_d_headache,
              yes_avg_d_eyestrain,
              yes_avg_d_sweating,
              yes_avg_d_nausea,
              yes_avg_d_dizziness_c,
              yes_avg_d_dizziness_o,
              yes_avg_d_difficulty_focusing,
              yes_avg_d_difficulty_concentrating,
              yes_avg_d_salivation,
              yes_avg_d_vision,
              yes_avg_d_vertigo,
              yes_avg_d_stomach,
              yes_avg_d_fullness,
              yes_avg_d_burping
              )

no_means = c(no_avg_d_discomfort,
             no_avg_d_fatigue,
             no_avg_d_headache,
             no_avg_d_eyestrain,
             no_avg_d_sweating,
             no_avg_d_nausea,
             no_avg_d_dizziness_c,
             no_avg_d_dizziness_o,
             no_avg_d_difficulty_focusing,
             no_avg_d_difficulty_concentrating,
             no_avg_d_salivation,
             no_avg_d_vision,
             no_avg_d_vertigo,
             no_avg_d_stomach,
             no_avg_d_fullness,
             no_avg_d_burping
             )

fig <- plot_ly(
  type  = 'scatterpolar',
  fill = 'toself',
  title = "Average change in BSSQ and ASSQ depending on VR experience for each symptom"
)

fig <- fig %>% 
  add_trace(
    r = yes_means,
    theta = c('Discomfort', 'Fatigue', 'Headache', 'Eyestrain', 'Sweating', 'Nausea', 'Dizziness (closed)', 'Dizziness (open)', 'Difficulty Focusing', 'Difficulty Concentrating', 'Salivation', 'Blurry Vision', 'Vertigo', 'Stomach Awareness', 'Fullness of head','Burping'),
    name = 'With VR Experience'
  )

fig <- fig %>% 
  add_trace(
    r = no_means,
    theta = c('Discomfort', 'Fatigue', 'Headache', 'Eyestrain', 'Sweating', 'Nausea','Dizziness (closed)', 'Dizziness (open)', 'Difficulty Focusing', 'Difficulty Concentrating', 'Salivation', 'Blurry Vision',  'Vertigo', 'Stomach Awareness', 'Fullness of head','Burping'),
    name = 'No VR Experience'
  )

fig <- fig %>%
  layout(
    polar = list(
      radialaxis = list(
        visible = T,
        range = c(-0.5,2)
      )
    ),
    showlegend = T
  )

fig
```

The spider-chart above reinforces what we see in the box-plot, with VR experienced users all indicating a higher average $\Delta$ for almost all of the 16 symptoms.

These observations are in contrast to \[insert article(s) here\]

```{r}
ggplot(filteredData) +
  geom_boxplot(aes(x = "Discomfort", y = d_discomfort, fill = VRexperience)) +
  geom_boxplot(aes(x = "Fatigue", y = d_fatigue, fill = VRexperience)) +
  geom_boxplot(aes(x = "Headache", y = d_headache, fill = VRexperience)) +
  geom_boxplot(aes(x = "Eyestrain", y = d_eyestrain, fill = VRexperience)) +
  geom_boxplot(aes(x = "Difficulty Focusing", y = d_difficulty_focusing, fill = VRexperience)) +
  geom_boxplot(aes(x = "Salivation", y = d_salivation, fill = VRexperience)) +
  geom_boxplot(aes(x = "Sweating", y = d_sweating, fill = VRexperience)) +
  geom_boxplot(aes(x = "Nausea", y = d_nausea, fill = VRexperience)) +
  geom_boxplot(aes(x = "Difficulty Concentrating", y = d_difficulty_concentrating, fill = VRexperience)) +
  geom_boxplot(aes(x = "Fullness of Head", y = d_fullness_of_head, fill = VRexperience)) +
  geom_boxplot(aes(x = "Blurred Vision", y = d_blurred_vision, fill = VRexperience)) +
  geom_boxplot(aes(x = "Dizziness (o)", y = d_dizziness_o, fill = VRexperience)) +
  geom_boxplot(aes(x = "Dizziness (c)", y = d_dizziness_c, fill = VRexperience)) +
  geom_boxplot(aes(x = "Vertigo", y = d_vertigo, fill = VRexperience)) +
  geom_boxplot(aes(x = "Stomach Awareness", y = d_stomach_awareness, fill = VRexperience)) +
  theme_minimal() +
  labs(title = "VR Experience and Symptom Change",
       x = "Symptom",
       y = "Change in Severity") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

```{r}
library(tidyverse)
library(plotly)

plt = ggplot(filteredData, aes(x = as.factor(gender) , y = ssq_full, group = VRexperience, fill = VRexperience)) +
  geom_boxplot(position = "dodge") +
  labs(x = "gender",  y = "Full SSQ")
plt

ggplotly(plt) %>%  layout(boxmode = "group")
```

::: panel-tabset
## Dizziness

```{r}
#| label: Dizziness Boxplot 
library(tidyverse)
library(plotly)

plt = ggplot(filteredData, aes(x = VRexperience, y = d_dizziness_c)) +
  geom_boxplot() +
  labs(x = "VR Experience",  y = "Change in BSSQ and ASSQ-Dizziness (Eyes Closed)")

ggplotly(plt)

#fivenum(withVRexperience$d_dizziness_c)
#fivenum(noVRexperience$d_dizziness_c)
#
#mean(withVRexperience$d_dizziness_c)
#mean(noVRexperience$d_dizziness_c)
#
#sd(withVRexperience$d_dizziness_c)
#sd(noVRexperience$d_dizziness_c)


#since from the boxplots we can see that both sets have a fair number of outliers which could affect the mean, the median + IQR may be a better measure of spread

```

```{r}
#| label: Dizziness Scatterplot
#| message: false
#| warning: false
library(tidyverse)
library(plotly)
library(gganimate)
library(gifski)

plt = ggplot(filteredData, aes(y = d_dizziness_c, x = age, colour = VRexperience)) +
  geom_point() +
  labs(x = "Age",  y = "Dizziness (Eyes Closed)", col = "VR Experience") +
  transition_states(VRexperience, transition_length = 1, state_length = 1) +
  enter_fade() + exit_fade()

#animate(plt, renderer = gifski_renderer())
ggplotly(plt)
```

```{r}
#| label: Age groups for dizziness boxplot
library(tidyverse)
library(plotly)

plt = ggplot(filteredData, aes(x = age_group, y = d_dizziness_c)) +
  geom_boxplot() +
  labs(x = "Age Group",  y = "Change in BSSQ and ASSQ-Dizziness(Eyes Closed)")

ggplotly(plt)

```

## Vertigo

```{r}
#| label: Vertigo boxplot
library(tidyverse)
library(plotly)

plt = ggplot(filteredData, aes(x = VRexperience, y = d_vertigo)) +
  geom_boxplot() +
  labs(x = "VR Experience",  y = "Vertigo")

ggplotly(plt)

#fivenum(withVRexperience$d_vertigo)
#fivenum(noVRexperience$d_vertigo)
#
#mean(withVRexperience$d_vertigo)
#mean(noVRexperience$d_vertigo)
#
#sd(withVRexperience$d_vertigo)
#sd(noVRexperience$d_vertigo)
```

```{r}
#| label: Age groups for vertigo boxplot
library(tidyverse)
library(plotly)

plt = ggplot(filteredData, aes(x = age_group, y = d_vertigo)) +
  geom_boxplot() +
  labs(x = "Age Group",  y = "Change in BSSQ and ASSQ - Vertigo")

ggplotly(plt)
```

```{r}
#| label: Vertigo Scatterplot
#| message: false
#| warning: false
library(tidyverse)
library(plotly)
library(gganimate)
library(gifski)

plt = ggplot(filteredData, aes(y = d_vertigo, x = age, colour = VRexperience)) +
  geom_point() +
  labs(x = "Age",  y = "Vertigo", col = "VR Experience") +
  transition_states(VRexperience, transition_length = 1, state_length = 1) +
  enter_fade() + exit_fade()

#animate(plt, renderer = gifski_renderer())
ggplotly(plt)
```

## Stomach Awareness

```{r}
#| label: Stomach_awareness boxplot
#| message: false
#| warning: false
library(tidyverse)
library(plotly)

plt = ggplot(filteredData, aes(x = VRexperience, y = d_stomach_awareness)) +
  geom_boxplot() +
  labs(x = "VR Experience",  y = "Change in BSSQ and ASSQ - Stomach Awareness")

ggplotly(plt)

```

```{r}
#| label: Age groups for stomach awareness boxplot
library(tidyverse)
library(plotly)

plt = ggplot(filteredData, aes(x = age_group, y = d_stomach_awareness)) +
  geom_boxplot() +
  labs(x = "Age Group",  y = "Change in BSSQ and ASSQ - Stomach Awareness")

ggplotly(plt)
```

```{r}
#| label: Stomach Awareness Scatterplot
#| message: false
#| warning: false
library(tidyverse)
library(plotly)
library(gganimate)
library(gifski)

plt = ggplot(filteredData, aes(y = d_stomach_awareness, x = age, colour = VRexperience)) +
  geom_point() +
  labs(x = "Age",  y = "Stomach Awareness", col = "VR Experience") +
  transition_states(VRexperience, transition_length = 1, state_length = 1) +
  enter_fade() + exit_fade()

#animate(plt, renderer = gifski_renderer())
ggplotly(plt)
```
:::

```{r}
library(plotly)
library(tidyselect)

mean_sqq_ages = c(mean(grp1$ssq_full),
                  mean(grp2$ssq_full),
                  mean(grp3$ssq_full),
                  mean(grp4$ssq_full),
                  mean(grp5$ssq_full)
                  )

fig2 <- plot_ly(
  type = 'scatterpolar',
  fill = 'toself',
  r = mean_sqq_ages,
  theta = c("16 to 21",
            "22 to 29",
            "30 to 37",
            "38 to 45",
            "above 45")
)
fig2 <- fig2 %>%
  layout(
    polar = list(
      radialaxis = list(
        visible = T,
        range = c(0,20)
      )
    ),
    showlegend = T
  )

fig2

fig3 = ggplot(data_by_age_group, aes(x = age_group, y = mean_ssq)) +
  geom_bar(stat = 'identity')



ggplotly(fig3)
```

```{r}
library(tidyverse)

p = ggplot(filteredData, aes(x = age, y = ssq_full, colour = VRexperience)) +
  geom_point()

p
```

```{r}
plt = ggplot(filteredData, aes(x = VRexperience, y = ssq_full, fill = VRexperience)) +
  geom_boxplot() +
  theme_minimal()

ggplotly(plt)
```

```{r}
plt2 = ggplot(filteredData, aes(x = age_group, y = ssq_full)) +
  geom_boxplot()

ggplotly(plt2)
```

```{r}
#| warning: false
library(tidyverse)

yex = filter(filteredData, VRexperience == "Yes")
nox = filter(filteredData, VRexperience == "No")

q1 = quantile(yex$age, probs = c(0.25), na.rm = TRUE) |> as.numeric()
q2 = quantile(nox$age, probs = c(0.25), na.rm = TRUE) |> as.numeric()
# https://forum.posit.co/t/make-the-r-function-quantile-return-a-numeric-value/178084
q3 = 2*q2-q1

ggplot(filteredData, aes(x = VRexperience, y = age)) + geom_boxplot() + geom_hline(yintercept = q1) + geom_hline(yintercept = q2) + geom_hline(yintercept = q3)

filteredData = mutate(filteredData, age_class = case_when(age > q3 ~ "older",
                                                      age > q2 ~ "old",
                                                      age > q1 ~ "young",
                                                      age > 0 ~ "younger"))

ggplot(filter(filteredData, age_class == "old" | age_class == "young"), aes(x = age_class, y = ssq_full)) + geom_boxplot()
```

```{r}
filteredData["age_group"] = cut(filteredData$age, c(16, 22, 30, 38, 46, Inf), c("16-21", "22-29", "30-37", "38-45", "45+"), include.lowest = TRUE)

ggplot(filteredData, aes(x = VRexperience, y = ssq_full, fill = VRexperience)) + stat_summary(fun = "mean", geom = "bar", position = "dodge")
```

```{r}
library(lubridate)

class(filteredData$Date[1])
d = filteredData$Date[1] |> as.POSIXct()
year(d) # used chatgpt for this because there is no known website in the universe that has this information for SOME REASON

ggplot(filteredData, aes(x = generation, y = ssq_full)) + geom_boxplot()
ggplot(filteredData, aes(x = age, y = ssq_full, color = generation)) + geom_point()
```

# Professional Standard of Report

# Acknowledgements

# References
