---
title: "DATA1901 Project 1 Group 5 Submission"
format: 
  html: 
    embed-resources: true
    code-fold: true
    df_print: paged
editor: visual
theme: lux
---

```{r}
#| message: false
#| warning: false
suppressPackageStartupMessages(library(readxl))
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(plotly))
suppressPackageStartupMessages(library(fmsb))

data = read_excel("Project_1_Data.xlsx", sheet = "pooled123")

filteredData = select(data, Date, PID, BSSQ_1:BSSQ_16, ASSQ_1:ASSQ_16, age, VRexperience, ssq_full, gender, sm)
#we only want to look at those that did not undergo social modelling conditions
filteredData = subset(filteredData, sm == "NO_SM")

#calculating differences between baseline and active SSQ for each symptom
filteredData = mutate(filteredData, d_discomfort = ASSQ_1 - BSSQ_1)
filteredData = mutate(filteredData, d_fatigue = ASSQ_2 - BSSQ_2)
filteredData = mutate(filteredData, d_headache = ASSQ_3 - BSSQ_3)
filteredData = mutate(filteredData, d_eyestrain = ASSQ_4 - BSSQ_4)
filteredData = mutate(filteredData, d_difficulty_focusing = ASSQ_5 - BSSQ_5)
filteredData = mutate(filteredData, d_salivation = ASSQ_6 - BSSQ_6)
filteredData = mutate(filteredData, d_sweating = ASSQ_7 - BSSQ_7)
filteredData = mutate(filteredData, d_nausea = ASSQ_8 - BSSQ_8)
filteredData = mutate(filteredData, d_difficulty_concentrating = ASSQ_9 - BSSQ_9)
filteredData = mutate(filteredData, d_fullness_of_head = ASSQ_10 - BSSQ_10)
filteredData = mutate(filteredData, d_blurred_vision = ASSQ_11 - BSSQ_11)
filteredData = mutate(filteredData, d_dizziness_o = ASSQ_12 - BSSQ_12)
filteredData = mutate(filteredData, d_dizziness_c = ASSQ_13 - BSSQ_13)
filteredData = mutate(filteredData, d_vertigo = ASSQ_14 - BSSQ_14)
filteredData = mutate(filteredData, d_stomach_awareness = ASSQ_15 - BSSQ_15)
filteredData = mutate(filteredData, d_burping = ASSQ_16 - BSSQ_16)

#reclasss VR experience as factor (was chr)
filteredData$VRexperience = as.factor(filteredData$VRexperience)

#we want to filter this data even further and split it into age groups
#once in age groups, calculate the mean change for each of the age groups for each symptom
filteredData = mutate(filteredData, age_group = case_when(
  age >= 16 & age <= 21 ~ "16 to 21",
  age >= 22 & age <= 29 ~ "22 to 29",
  age >= 30 & age <= 37 ~ "30 to 37",
  age >= 38 & age <= 45 ~ "38 to 45",
  age > 45 ~ "above 45"
))

#convert the age groups into factors
filteredData$age_group = as.factor(filteredData$age_group)

#renaming columns to be more informative
names(filteredData)[names(filteredData) == 'BSSQ_1'] <- 'BSSQ_discomfort'
names(filteredData)[names(filteredData) == 'BSSQ_2'] <- 'BSSQ_fatigue'
names(filteredData)[names(filteredData) == 'BSSQ_3'] <- 'BSSQ_headache'
names(filteredData)[names(filteredData) == 'BSSQ_4'] <- 'BSSQ_eyestrain'
names(filteredData)[names(filteredData) == 'BSSQ_5'] <- 'BSSQ_difficulty_focusing'
names(filteredData)[names(filteredData) == 'BSSQ_6'] <- 'BSSQ_salivation'
names(filteredData)[names(filteredData) == 'BSSQ_7'] <- 'BSSQ_sweating'
names(filteredData)[names(filteredData) == 'BSSQ_8'] <- 'BSSQ_nausea'
names(filteredData)[names(filteredData) == 'BSSQ_9'] <- 'BSSQ_difficulty_concentrating'
names(filteredData)[names(filteredData) == 'BSSQ_10'] <- 'BSSQ_fullness_of_head'
names(filteredData)[names(filteredData) == 'BSSQ_11'] <- 'BSSQ_blurred_vision'
names(filteredData)[names(filteredData) == 'BSSQ_12'] <- 'BSSQ_dizziness_o'
names(filteredData)[names(filteredData) == 'BSSQ_13'] <- 'BSSQ_dizziness_c'
names(filteredData)[names(filteredData) == 'BSSQ_14'] <- 'BSSQ_vertigo'
names(filteredData)[names(filteredData) == 'BSSQ_15'] <- 'BSSQ_stomach_awareness'
names(filteredData)[names(filteredData) == 'BSSQ_16'] <- 'BSSQ_burping'

names(filteredData)[names(filteredData) == 'ASSQ_1'] <- 'ASSQ_discomfort'
names(filteredData)[names(filteredData) == 'ASSQ_2'] <- 'ASSQ_fatigue'
names(filteredData)[names(filteredData) == 'ASSQ_3'] <- 'ASSQ_headache'
names(filteredData)[names(filteredData) == 'ASSQ_4'] <- 'ASSQ_eyestrain'
names(filteredData)[names(filteredData) == 'ASSQ_5'] <- 'ASSQ_difficulty_focusing'
names(filteredData)[names(filteredData) == 'ASSQ_6'] <- 'ASSQ_salivation'
names(filteredData)[names(filteredData) == 'ASSQ_7'] <- 'ASSQ_sweating'
names(filteredData)[names(filteredData) == 'ASSQ_8'] <- 'ASSQ_nausea'
names(filteredData)[names(filteredData) == 'ASSQ_9'] <- 'ASSQ_difficulty_concentrating'
names(filteredData)[names(filteredData) == 'ASSQ_10'] <- 'ASSQ_fullness_of_head'
names(filteredData)[names(filteredData) == 'ASSQ_11'] <- 'ASSQ_blurred_vision'
names(filteredData)[names(filteredData) == 'ASSQ_12'] <- 'ASSQ_dizziness_o'
names(filteredData)[names(filteredData) == 'ASSQ_13'] <- 'ASSQ_dizziness_c'
names(filteredData)[names(filteredData) == 'ASSQ_14'] <- 'ASSQ_vertigo'
names(filteredData)[names(filteredData) == 'ASSQ_15'] <- 'ASSQ_stomach_awareness'
names(filteredData)[names(filteredData) == 'ASSQ_16'] <- 'ASSQ_burping'


#isolating the data dictionary
data_dict = read_excel("Project_1_Data.xlsx", sheet = "data_dictionary")

#filter into groups with experience or not
withVRexperience = filter(filteredData, VRexperience == 'Yes')
noVRexperience = filter(filteredData, VRexperience == 'No')

#taking averages for with/without experience
yes_avg_d_discomfort = mean(withVRexperience$d_discomfort)
yes_avg_d_fatigue = mean(withVRexperience$d_fatigue)
yes_avg_d_headache = mean(withVRexperience$d_headache)
yes_avg_d_eyestrain = mean(withVRexperience$d_eyestrain)
yes_avg_d_difficulty_focusing = mean(withVRexperience$d_difficulty_focusing)
yes_avg_d_salivation = mean(withVRexperience$d_salivation)
yes_avg_d_sweating = mean(withVRexperience$d_sweating)
yes_avg_d_nausea = mean(withVRexperience$d_nausea)
yes_avg_d_difficulty_concentrating = mean(withVRexperience$d_difficulty_concentrating)
yes_avg_d_fullness = mean(withVRexperience$d_fullness_of_head)
yes_avg_d_vision = mean(withVRexperience$d_blurred_vision)
yes_avg_d_dizziness_o = mean(withVRexperience$d_dizziness_o)
yes_avg_d_dizziness_c = mean(withVRexperience$d_dizziness_c)
yes_avg_d_vertigo = mean(withVRexperience$d_vertigo)
yes_avg_d_stomach = mean(withVRexperience$d_stomach_awareness)
yes_avg_d_burping = mean(withVRexperience$d_burping)


no_avg_d_discomfort = mean(noVRexperience$d_discomfort)
no_avg_d_fatigue = mean(noVRexperience$d_fatigue)
no_avg_d_headache = mean(noVRexperience$d_headache)
no_avg_d_eyestrain = mean(noVRexperience$d_eyestrain)
no_avg_d_difficulty_focusing = mean(noVRexperience$d_difficulty_focusing)
no_avg_d_salivation = mean(noVRexperience$d_salivation)
no_avg_d_sweating = mean(noVRexperience$d_sweating)
no_avg_d_nausea = mean(noVRexperience$d_nausea)
no_avg_d_difficulty_concentrating = mean(noVRexperience$d_difficulty_concentrating)
no_avg_d_fullness = mean(noVRexperience$d_fullness_of_head)
no_avg_d_vision = mean(noVRexperience$d_blurred_vision)
no_avg_d_dizziness_o = mean(noVRexperience$d_dizziness_o)
no_avg_d_dizziness_c = mean(noVRexperience$d_dizziness_c)
no_avg_d_vertigo = mean(noVRexperience$d_vertigo)
no_avg_d_stomach = mean(noVRexperience$d_stomach_awareness)
no_avg_d_burping = mean(noVRexperience$d_burping)


#taking averages for different age groups
grp1 = filter(filteredData, age_group == '16 to 21')
grp2 = filter(filteredData, age_group == '22 to 29')
grp3 = filter(filteredData, age_group == '30 to 37')
grp4 = filter(filteredData, age_group == '38 to 45')
grp5 = filter(filteredData, age_group == 'above 45')

mean_sqq_ages = c(mean(grp1$ssq_full),
                  mean(grp2$ssq_full),
                  mean(grp3$ssq_full),
                  mean(grp4$ssq_full),
                  mean(grp5$ssq_full)
                  )

data_by_age_group = data.frame(
  age_group = c("16 to 21", '22 to 29','30 to 37','38 to 45','Above 45'),
  mean_ssq = mean_sqq_ages
  
)

filteredData = mutate(filteredData, "generation" = case_when(year(Date) - age >= 2010 ~ "a", year(Date) - age >= 1997 ~ "Z", year(Date) - age >= 1981 ~ "Y", year(Date) - age >= 1965 ~ "X", TRUE ~ "Old"))

```

## Summary of Findings

Our analysis found that individuals with prior VR experience reported heightened symptoms of motion sickness when exposed to VR, compared to those without experience. Age and gender had little to no effect on results. Further research should examine the nature, amount, and frequency of prior VR use to improve accuracy.

## Initial Data Analysis (IDA)

**Source**

The data was sourced from Cosette Saunder's paper "[Socially Acquired Nocebo Effects Generalize but Are Not Attenuated by Choice](https://drive.google.com/file/d/1stc1Yj0-3ZDLqM31Mf-WKOIVdQYb4TkP/view)".

**Structure**

We specifically looked at participants that did not undergo any social modelling; 69 participants, each with 51 variables recorded. Our project focused the following variables:

-   Baseline SSQ (`BSSQ`), Active SSQ (`ASSQ`), and `SSQ_Full`of 16 symptoms (*quantitative, discrete)*: self-reported symptom severity before and after undergoing VR respectively, on a scale of 1 to 10.

-   Participants' `VRexperience` (*qualitative, nominal)*; sorted by experience to see how symptoms differed.

-   `age` of participants (quantitative*, discrete)*; they were then sorted into `age groups`.

-   The change ($\Delta$) between `BSSQ` and `ASSQ` was calculated for each participant for each symptom, and we took the average $\Delta$ for each symptom for each group (`VRexperience` and `age_group`) (*quantitative, discrete).*

::: panel-tabset
## Age Groups

```{r}
#| label: Age groups pie chart
data_age_groups = select(filteredData, age_group)
groups_counted = data_age_groups %>% count(age_group)

age_pie = plot_ly(groups_counted, labels = ~age_group, values = ~n,
                 type = 'pie', direction = 'clockwise', sort = FALSE, rotation = 30, marker = list(colors = c("#A8DADC", "#FFD6A5", "#FDFFB6", "#BDE0FE")))
age_pie <- age_pie %>% layout(title = 'Distribution of ages',
                            showlegend = TRUE,
                            legend = list(title = list(text = "Age Group")))
age_pie
```

## VR Experience

```{r}
#| label: VR experience pie chart

data_experience = select(filteredData, VRexperience)
exp_counted = data_experience %>% count(VRexperience)

vr_pie = plot_ly(exp_counted, labels = ~VRexperience, values = ~n,
                 type = 'pie', marker = list(colors = c("#FDFFB6", "#BDE0FE")))
vr_pie <- vr_pie %>% layout(title = 'Distribution of VR experience',
                            showlegend = TRUE, legend = list(title = list(text = "VR experience")))

vr_pie

```

## VR Experience Age Groups

```{r}
#| label: Distribution of age groups for those with VR experience

data_experience = select(withVRexperience, age_group)
exp_counted = data_experience %>% count(age_group)

vr_pie = plot_ly(exp_counted, labels = ~age_group, values = ~n,
                 type = 'pie',marker = list(colors = c("#A8DADC", "#FFD6A5", "#FDFFB6", "#BDE0FE")))
vr_pie <- vr_pie %>% layout(title = 'Distribution of age groups for those with VR experience',
                            showlegend = TRUE, legend = list(title = list(text = "Age group")))

vr_pie

```

## No Experience Age Groups

```{r}
#| label: Distribution of age groups for those without VR experience

data_experience = select(noVRexperience, age_group)
exp_counted = data_experience %>% count(age_group)

vr_pie = plot_ly(exp_counted, labels = ~age_group, values = ~n,
                 type = 'pie', marker = list(colors = c("#A8DADC", "#FFD6A5", "#FDFFB6", "#BDE0FE")))
vr_pie <- vr_pie %>% layout(title = 'Distribution of age groups for those without VR experience',
                            showlegend = TRUE, legend = list(title = list(text = "Age group")))

vr_pie
```
:::

**Limitations**

-   *Self-reporting bias* for both `BSSQ` and `ASSQ` which makes the values prone to being over or underestimates by each participant.

-   `VRexperience` is a binary qualitative classification, it is not descriptive of the nature, amount or frequency, and that those with more than 10 VR experiences were excluded.

# [Research Question]{.underline}

## **Does past VR experience affect the symptoms experienced by people after a virtual reality experience?**

```{r}
#| label: Boxplot of full_ssq vs experience
#| message: false
#| warning: false

plt = ggplot(filteredData, aes(x = VRexperience, y = ssq_full, fill = VRexperience)) +
  geom_boxplot() +
  theme_minimal() +
  labs(x = "VR Experience", y = "Full SSQ") + scale_fill_manual(values = c("#A8DADC", "#FFD6A5")) +
  theme(legend.position = "none")
ggplotly(plt)
```

Participants with and without VR experience reported varied severity of symptoms. Interestingly, the VR-experienced group saw a greater median `ssq_full` and IQR, pointing to less consistent severity of symptoms. The group with VR experience also saw a higher mean value, contrasting previous research suggesting users with VR experience undergo less motion sickness (Chattha et al., 2020). This could be due to the smaller sample size of our data, wherein the symptoms vary too significantly for strong correlations to be found and random chance has noticable effect. Additionally, users who have experienced motion sickness in VR before may anticipate feeling sick again, leading to heightened symptoms, similar to a placebo.

```{r}
#| label: Experience and symptoms spider chart
#| message: false
#| warning: false
library(plotly)

yes_means = c(yes_avg_d_discomfort,
              yes_avg_d_fatigue,
              yes_avg_d_headache,
              yes_avg_d_eyestrain,
              yes_avg_d_sweating,
              yes_avg_d_nausea,
              yes_avg_d_dizziness_c,
              yes_avg_d_dizziness_o,
              yes_avg_d_difficulty_focusing,
              yes_avg_d_difficulty_concentrating,
              yes_avg_d_salivation,
              yes_avg_d_vision,
              yes_avg_d_vertigo,
              yes_avg_d_stomach,
              yes_avg_d_fullness,
              yes_avg_d_burping
              )

no_means = c(no_avg_d_discomfort,
             no_avg_d_fatigue,
             no_avg_d_headache,
             no_avg_d_eyestrain,
             no_avg_d_sweating,
             no_avg_d_nausea,
             no_avg_d_dizziness_c,
             no_avg_d_dizziness_o,
             no_avg_d_difficulty_focusing,
             no_avg_d_difficulty_concentrating,
             no_avg_d_salivation,
             no_avg_d_vision,
             no_avg_d_vertigo,
             no_avg_d_stomach,
             no_avg_d_fullness,
             no_avg_d_burping
             )

fig <- plot_ly(
  type  = 'scatterpolar',
  fill = 'toself',
  title = "Average change in BSSQ and ASSQ depending on VR experience for each symptom"
)

fig <- fig %>% 
  add_trace(
    r = yes_means,
    theta = c('Discomfort', 'Fatigue', 'Headache', 'Eyestrain', 'Sweating', 'Nausea', 'Dizziness (closed)', 'Dizziness (open)', 'Difficulty Focusing', 'Difficulty Concentrating', 'Salivation', 'Blurry Vision', 'Vertigo', 'Stomach Awareness', 'Fullness of head','Burping'),
    name = 'With VR Experience'
  )

fig <- fig %>% 
  add_trace(
    r = no_means,
    theta = c('Discomfort', 'Fatigue', 'Headache', 'Eyestrain', 'Sweating', 'Nausea','Dizziness (closed)', 'Dizziness (open)', 'Difficulty Focusing', 'Difficulty Concentrating', 'Salivation', 'Blurry Vision',  'Vertigo', 'Stomach Awareness', 'Fullness of head','Burping'),
    name = 'No VR Experience'
  )

fig <- fig %>%
  layout(
    polar = list(
      radialaxis = list(
        visible = T,
        range = c(-0.5,2)
      )
    ),
    showlegend = T,
    title = "Change in Symptoms by VRexperience",
    margin = c(5,5,5,5),
    legend = list(title = list(text = "VR experience"))
  )

fig
```

The spider-chart above reinforces what we see in the box-plot, with VR experienced users indicating a higher average $\Delta$ for almost all of the 16 symptoms.

To further investigate why our conclusion contradicts research, we stratified our analysis using a potential confounding variable: age.

::: panel-tabset
## With Experience

```{r}
plt2 = ggplot(withVRexperience, aes(x = age_group, y = ssq_full, fill = age_group)) +
  geom_boxplot() +
  labs(title = "Full SSQ for each age group (With experience)", y = "Full SSQ", x = "Age Group") +
  ylim(-10, 60) + scale_fill_manual(values = c("#A8DADC", "#FFD6A5", "#FDFFB6", "#BDE0FE")) +
  theme(legend.position = "none")

ggplotly(plt2)
```

## No Experience

```{r}
plt2 = ggplot(noVRexperience, aes(x = age_group, y = ssq_full, fill = age_group)) +
  geom_boxplot() +
  labs(title = "Full SSQ Scores for each age group (No experience)", y = "Full SSQ", x = "Age Group") +
  ylim(-10, 60) + scale_fill_manual(values = c("#A8DADC", "#FFD6A5", "#FDFFB6", "#BDE0FE")) +
  theme(legend.position = "none")

ggplotly(plt2)
```

## Comparison

```{r}
#| message: false
#| warning: false
library(tidyverse)
library(plotly)

plt = ggplot(filteredData, aes(x = as.factor(age_group) , y = ssq_full, group = VRexperience, fill = VRexperience)) +
  geom_boxplot(position = "dodge") +
  labs(x = "Age Group",  y = "Full SSQ", title = "Full SSQ Scores by Age Group (both groups)") +
  ylim(-10, 60) + scale_fill_manual(values = c("#A8DADC", "#FFD6A5", "#FDFFB6", "#BDE0FE"))

ggplotly(plt) %>%  layout(boxmode = "group")
```

## Combined

```{r}
plt2 = ggplot(filteredData, aes(x = age_group, y = ssq_full, fill = age_group)) +
  geom_boxplot() +
  labs(title = "Full SSQ Scores for each age group", y = "Full SSQ", x = "Age Group") +
  ylim(-10, 60) + scale_fill_manual(values = c("#A8DADC", "#FFD6A5", "#FDFFB6", "#BDE0FE")) +
  theme(legend.position = "none")

ggplotly(plt2)
```
:::

There appears to be substantial overlap between the box plots of SSQ scores across different age groups, even when filtered by experience. In both sets of graphs, the medians remain relatively close, with no consistent trend among the groups.

Notably, while SSQ spread varies, there seems to be no consistent pattern across the groups themselves. Though as expected, the spread and medians are much lower for the ‘No Experience’ condition.

These observations conflict with prior research suggesting older users experience more severe cyber-sickness (Oh & Son, 2022), possibly due to our data having unequal sample sizes across age groups. Namely, there are 29 participants in the 30-37 age group but only 7 in the 16-21 age group. This limits the reliability of comparisons.

Finally, we filtered by gender to investigate it as a potential confounder.

::: panel-tabset
## Comparison

```{r}
#| message: false
#| warning: false
library(tidyverse)
library(plotly)

plt = ggplot(filteredData, aes(x = as.factor(gender) , y = ssq_full, group = VRexperience, fill = VRexperience)) +
  geom_boxplot() +
  labs(x = "Gender",  y = "Full SSQ") + scale_fill_manual(values = c("#A8DADC", "#FFD6A5"))

ggplotly(plt) %>% layout(boxmode = "group")
```

## Combined

```{r}
#| message: false
#| warning: false
library(tidyverse)
library(plotly)

plt = ggplot(filteredData, aes(x = as.factor(gender) , y = ssq_full, fill = gender)) +
  geom_boxplot() +
  labs(x = "Gender",  y = "Full SSQ") + scale_fill_manual(values = c("#A8DADC", "#FFD6A5")) +
  theme(legend.position = "none")

ggplotly(plt)
```
:::

The box plots above indicate that females with VR experience report greater symptoms, agreeing with online research “*indicat\[ing\] excruciating symptoms of motion sickness in females*” (Chattha et al., 2020), but for participants without VR experience our data contradicts this conclusion—overall, we found little difference between genders.

# Professional Standard of Report

We maintained a shared value of respect as we respected the privacy of others and the promises of confidentiality given to them as the data we used was anonymous. We obeyed ethical principles by pursuing objectivity as we presented all findings holistically, and in a transparent manner irrespective of outcomes.

# Acknowledgements

## Group Meetings

*13 March, 13:00*

In attendance: Viet, Borna, Gokul (Ryan), Mohamed

We confirmed our research question and the variables we will be using for analysis, discussed our ideas on what types of graphs we can use to present the data, and decided on roles for our group members to take up over the next few weeks.

We also had group discussions at every Tuesday workshop where we would discuss progress we have made over the past week, what has been completed, what still needs to be completed and our plan of action for the next week.

## Resources Used

Our group collaborated on the project using GitHub (<https://github.com/uncoolbeans/DATA1901_project_1>)

Additionally, for our IDA and to make charts using R, we accessed documentation for:

-   The R Language: <https://www.rdocumentation.org/>

-   Plot_ly Graphing Library for R: <https://plotly.com/r/>

-   ggplot2 from Tidyverse: <https://ggplot2.tidyverse.org/>

## AI Usage

AI (ChatGPT) was used to clean up our code for one version pushed to GitHub. This was overwritten in subsequent versions. In our final submission, there is no use of any AI.

## Drop-in Sessions

Our group sent a representative (Ryan) for a drop-in session at Carslaw 535 at *3pm on April 10th* to get some feedback regarding the depth of our graphs and if they were enough to back up our analysis points. We received feedback that we should include more titles and label our legend for the graphs, which we subsequently implemented.

# References

Chattha, U. A., Janjua, U. I., Anwar, F., Madni, T. M., Cheema, M. F., & Janjua, S. I. (2020). Motion Sickness in Virtual Reality: An Empirical Evaluation. *IEEE Access*, *8*, 130486–130499. <https://doi.org/10.1109/access.2020.3007076>

‌Oh, H., & Son, W. (2022). Cybersickness and Its Severity Arising from Virtual Reality Content: A Comprehensive Study. *Sensors*, *22*(4), 1314. <https://doi.org/10.3390/s22041314>

‌
